\documentclass[11pt]{article}
\pagenumbering{gobble}
\usepackage[skip=9pt plus1pt]{parskip}
\usepackage[hmargin=20mm, top=14mm, bottom=12mm]{geometry} % US letter; matches cv.tex
\usepackage{hyperref}

%---------------------------------------------------------------------------------------
%  Fill these in per application
%---------------------------------------------------------------------------------------
\newcommand{\company}{Epic Games}
\newcommand{\role}{Senior Language Engineer}
\newcommand{\greeting}{To whom it may concern}

\begin{document}

%---------------------------------------------------------------------------------------
%  Letterhead (matches cv.tex)
%---------------------------------------------------------------------------------------
\parbox{0.5\textwidth}{
\huge{\textbf{Minsung Cho}}
}
\hfill
\parbox{0.5\textwidth}{
\begin{tabbing}
\hspace{3cm} \= \hspace{4cm} \= \kill
\href{mailto:minsungc1@gmail.com}{\texttt{minsungc1@gmail.com}} \\
\href{https://linkedin.com/in/minsung-c}{linkedin.com/in/minsung-c}
\end{tabbing}}

\hrule
\vspace{1.5em}

\today

\vspace{1em}

\noindent \greeting{},

I'm excited to apply for the \role{} position at \company{}. I read the Verse
paper in graduate school, and I was glad to see a role open in my home of New York City.
Currently, I work on logic programming compilers for databases, and am interested in
seeing it applied in other domains.

At RelationalAI, I lead the design and implementation of extensions to our Datalog-based 
declarative query
language. This includes an imperative, procedural-style sublanguage and a GQL-style graph
pattern-matching extension. I also maintain the database engine's primary entry point, which
serves roughly 100k queries per day. The work spans the ``full stack" of compilers:
from designing syntax based on customer feedback and working out the semantics of the language,
to writing optimization passes and
scaffolding the tooling and observability needed to debug all of it. In the short span of a year,
my work has already been adopted by our largest enterprise customers as well as
played a pivotal role in procuring new ones.

This engineering is grounded in programming languages research, much like Verse.
I designed and published a probabilistic programming language for optimization under uncertainty
at OOPSLA that outperforms the state of the art, and
I hold a master's in computer science from Northeastern's Programming Research Lab.
At \company{}, I'm looking forward to contributing to the development of a language
from theory to implementation at a scale larger than I have experienced so far.
I have a proven track record of this, and would love to get to know the team.

\vspace{1em}

\noindent Thank you for your consideration, \\
Minsung Cho

\end{document}
